Generalised gravitational burst generation with Generative Adversarial Networks

### 2020-07-27 Paper_draft/main.tex
Paper changes to cGAN

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/train_gen.pdf}
    \caption{Examples of simulated \ac{GW} burst signals. Top row shows
examples from the training set. From left to right: Sine-Gaussian, Ringdown,
White-noise burst, Gaussian pulse, Binary black hole merger. The bottom row
shows the conditional generations from the GAN. Each plots contains only one detector output for ease of viewing.}
\label{fig:train} \end{figure}

@@

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/gens+taining.eps}
    \caption{Generated waveforms after training and conditioning on five classes. The generator will output two waveforms as seen by detectors in Hanford (red) and Livingston (blue). The generator is able to capture the characteristics of each waveform and structure the class space to give control over which waveform to generate. Each row shows a random assortment of one of the five classes the GAN is trained on. }
    \label{fig:gen_signals}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/z_interpolation.eps}
    \caption{Interpolations between two random latent points in z. Each row uniformly interpolates between two points in $\mathbf{z}$ keeping the class fixed. Only a single waveform from the generator is plotted and each signal is re-scaled to [-1,1] effectively removing the antenna responses for clarity.}
    \label{fig:z_interp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/class_interpolation.eps}
    \caption{Class space interpolation with latent space held constant throughout. The plots show a zoomed in section of the 1s time interval. First row: Sine-Gaussian class to ringdown class, Second Row: Sine-Gaussian class to whitenoise burst class, Third row: Sine-Gaussian class to Gaussian class, Fourth row: Sine-Gaussian to BBH class.}
    \label{fig:c_interp}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/sg_bbh_interp.pdf}
    \caption{Class space interpolation with latent space held constant throughout. The full 1s interval is plotted for class based interpolations between a Sine-Gaussian and a BBH in spiral.}
    \label{fig:sgbbh_interp}
\end{figure}

\begin{comment}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/4_corners.pdf}
    \caption{We generate the four corners of the grid, then interpolate between both the z and c vectors. Although the network was only trained on binary attributes for c, interpolation results show that the computed latent space is smooth between attributes, and not simply discrete to those shown in the training set.}
    \label{fig:4_c_interp}
\end{figure}
\end{comment}

@@

\begin{figure}
  \centering
  \begin{tabular}[b]{c}
    \includegraphics[width=0.9\textwidth]{figures/wn+bbh.pdf} \\
    \small ~~~~~~~~~(a)
  \end{tabular} %\qquad
  \begin{tabular}[b]{c}
    \includegraphics[width=0.46\textwidth]{figures/ambient_result.pdf} \\
    \small ~~~~~~~~(b)
  \end{tabular}
 \begin{tabular}[b]{c}
    \includegraphics[width=0.44\textwidth]{figures/arithmetic_result.pdf} \\
    \small ~~~~~~~~(c)
  \end{tabular}
  \caption{Conditional vector arithmetic. (a) Generated samples of a whitenoise burst and BBH insprial. (c) Effect of naively adding the components from (a) in the time domain. \jordan{just adding the two signals post generation} (c) Generation from the combined class vectors. }
  \label{fig:arithmetic}
\end{figure}

\begin{comment}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/arithm.pdf}
    \caption{Vector arithmetic for unmodelled waveforms. Keeping the z vectors constant and generating two classes of signals, their class embedding vectors can then be averaged to produce a new class. The generator produces a waveform of this hybrid class (middle of right plot). For the surrounding 8 plots we add a small variance of Gaussian noise to the new class. }
    \label{fig:add}
\end{figure}
\end{comment}
\subsection{Classifier}
\jordan{I'm working on this part and how to present the auxiliary part.}

>>>>

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/sg.png}
    \includegraphics[width=\textwidth]{figures/generations/rd.png}
    \includegraphics[width=\textwidth]{figures/generations/wnb.png}
    \includegraphics[width=\textwidth]{figures/generations/blip.png}
    \includegraphics[width=\textwidth]{figures/generations/bbh.png}
    \caption{Examples of \ac{GW} burst signals generated by a conditional generative adversarial network. Top row shows
examples from the training set. By row: Sine-Gaussian, Ringdown,
White-noise burst, Gaussian pulse, Binary black hole merger.}
\label{fig:train} \end{figure}

@@

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/generations/interp_rd-sg.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_wnb-blip.png}
    \includegraphics[width=\textwidth]{figures/generations/interp_sg-bbh.png}
    \caption{Latent space linear interpolation, class space is held constant.}
    \label{fig:c_interp}
\end{figure}

\subsection{Sampling from simplex section}

@@
